LME-MPM applied to quasi-brittle fracture.

### 2020-06-23 2020_EFM_MPM_Eigensoftening.tex
Cambios PNA

\documentclass[preprint,12pt,a4paper]{elsarticle}
\usepackage{lineno}
\usepackage{hyperref}
\usepackage{float}
\usepackage{graphicx} % figuras
% \usepackage{subfig}
\usepackage{subfigure} % subfiguras
\usepackage{multirow} 
\usepackage{color}
\usepackage{soul}
\usepackage{cancel}

@@

The simulation of fracture propagation in a more accurate and effective
way can be considered as one of the \PNA{ongoing goals} of the development of novel spatial discretization methods like meshfree techniques. Some
examples of it are the \acrfull{mpm}
\cite{Schreyer_2002,Chen_2002,Nairn_2003,Zhenmao_2005}, the
\acrfull{efgm} \cite{BELYTSCHKO_1995,BELYTSCHKO_2000,Zhuang_2012,Muthu_2013}, the
\acrfull{sph} \cite{Wang_2020,Wang_2019}, the \acrfull{otm} \cite{Li2010,Li_2012,Pandolfi_2013,Li_2015} or Peridynamics
\cite{HA_2011,RABCZUK_2017} among others. \\

\MMP{Concerning} \acrshort{mpm}, fracture \PNA{has been treated numerically through two different ways}. On the one hand, the ``CRAcks with Material Points (CRAMP)'' is proposed~\cite{Nairn_2003,Nairn_2006}. \PNA{The basis of this methodology consist of the removal of} the restriction
of the single-valued velocity field close to the crack through, at least, two sets of nodes. In this method, different labels are assigned to the material points
and nodes to distinguish if they are in the same side of the crack or
not. Under this approach, crack surface is described with line segments
in 2D and triangle patches in 3D cases. The chosen criteria for crack
propagation is based on such parameters as energy release rate
analyzed by Tan \& Nairn (2002)\cite{Nairn_2002}, and the stress
intensity factor or the J-integral discussed by Guo \& Nairn
(2004)\cite{Nairn_2004}. 
On the other hand, the \PNA{foundation} of the second approach is the introduction of failed
material points to describe the crack evolution. In these methods, the
formation of failed points describes the nucleation of cracks, and
thereafter its propagation and branching. Consequently, the position
of the crack does not need to be explicitly stated. This fact represents
significant advantages over the ``CRAMP''. Under this approach, the
prediction of failure evolution is computed with a decohesion model,
which has been discussed by Chen {\it et al.}\cite{Zhenmao_2005} and
Schreyer {\it et al.}\cite{Schreyer_2002}. Successful simulations are provided within the framework of the fracture of brittle materials by Chen {\it et
  al.} \cite{Chen_2002,Chen_2003} and Sulsky \& Schreyer
\cite{Sulsky_2004}.\\

Similar to this approach, Schmidt {\it et al.}
\cite{Schmidt_2009} introduced the concept of eigenfracture, where
crack sets are approximated by means of eigen-deformations, which
enable the material to develop displacement jumps at no cost of local
elastic energy. Later, the eigenerosion approach to brittle facture
was carried out by Pandolfi {\it et al.}
\cite{Pandolfi_2012,Pandolfi_2013}. \PNA{In this technique, the concept of ``erosion'' of
the material point is depicted, being the material point able to remain intact or become completely failed or eroded, when no loading
capacity is bore}. This method has been successfully applied to simulate high
complex phenomena such as dynamic fragmentation of metals
\cite{Li_2015}. Recently, Zhang {\it et al.}
\cite{Zhang_EE_2020} adopted the eigenerosion to resolve the dynamic
fracture of brittle materials in the \acrshort{mpm}
framework. Nonetheless, when quasi-brittle materials are simulated
though this approach, the results exhibit an overestimation of tensile
stress and strain peaks. Furthermore, since the work of Zhang {\it et al.}
\cite{Zhang_EE_2020} is made with conventional \acrshort{mpm}/\acrshort{gimp}, stress oscillations are to be faced.\\

To overcome the limitations observed in the EigenMPM
\cite{Zhang_EE_2020}, the present research proposes the eigensoftening
algorithm developed by Navas {\it et al.}
\cite{Navas_2017_ES,Navas2018a} for the \acrshort{otm} framework and
engineered for quasi-brittle materials. Inspired in the concept of the
crack band model \cite{Bazant83}, since energy dissipation is performed through the softened (or failed) volume, this methodology is able to capture the gradual rather than abrupt
dissipation of the fracture energy. \PNA{Moreover, in order to mitigate stress
oscillations as well as to deal with tensile instabilities, such those that
occurs when particles crosses an element boundary, the work of Molinos~\etal~\cite{Molinos2020} is followed. The traditional \acrshort{mpm} technique is enhanced through the \acrfull{lme} approximation technique
\cite{Arroyo2006} for the spatial discretization as well as a explicitly \acrshort{mpm} \acrfull{npc} scheme is derived for the time discretization.}\\

@@

regularization o \textit{thermalization} parameter such that for

@@

The failure criterion consist of considering that a material point is failed
when $G_p^{k+1}$ surpasses the critical energy release rate that
measures the material-specific energy, $G_F$. The convergence of this
approach has been analyzed by Schmidt {\it et al.}
(2009)\cite{Schmidt_2009}, who proved that $G_F$ converges to the Griffith
fracture when the discretization size tends to zero. It is necessary to
point out that, when a material point overpass the critical energy, its
contribution to the internal forces vector is set to zero, but its
contribution to the mass matrix is preserved.\\

@@

neighborhood of $\vec{x}_p^{k+1}$, the equation 

@@

\DM{The proposed approach to overcome the two main shortcomings of
  EighenMPM \cite{Zhang_EE_2020} has been evaluated with ``three
  benchmark tests''}.
The first one deals with the presence of stress
instabilities provoked by the spatial discretization, appearing even when the \acrshort{gimp} shape functions are employed. To overcome it, \acrshort{lme}
approximants are introduced as an alternative to the existing interpolation techniques. Its
performance in mitigating spurious stress oscillations under the \acrshort{mpm}~\cite{Wobbes2020,Molinos2020} framework helps to enhance
notoriously the quality of the results as it is observed in Section
\ref{sec:3.1}, where both interpolation techniques
are compared by carrying out an eigenerosion simulation. The second
limitation is concerned to its inability to simulate properly quasi-brittle
fracture \cite{Navas_2018_ES}. It can be solved through the
eigensoftening algorithm described in Section \ref{sec:2.3}.\MMP{A proof
of it is exposed in Sections \ref{sec:3.2} \ref{sec:3.3}, where experimental results
are compared with experimental ones as well as eigensoftening
computations. In the first case comparing with a semicircular bending
test and in the second case with a drop-weight impact test.}

\subsection{Edge-cracked square panel in mode I}
\label{sec:3.1}
The aim of the problem presented hereinafter is to assess the
capability of the \acrshort{lme} approximants to improve the result
\textit{versus} the standard linear interpolation. The application
consists of a square plate of size\MMP{$H = 1\ [L] $} containing an initial edge
crack of length $0.25 \cdot H$ loaded in a pure mode I by displacement
control on the outer flanks of the plate (See Figure
\ref{fig:geometry-cracked-panel-mode-I} for details). 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{Figure-Mode_I}
  \caption{Geometry and boundary condition of the drop-weight impact test.}
  \label{fig:geometry-cracked-panel-mode-I}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The constitutive model considered in the numerical experiment is a
linear-elastic Hookean material, whose Young's modulus \MMP{\gls{E} = 1.06
$[M] [L]^{-1} [T]^{-2}$, the Poisson's ratio \gls{nu} = 0.333, and
critical energy-release rate \gls{Gf} = 0.0001 $[L]^{2} [T]^{-2}$. The absence of units is due to the current simulation will not be validated against experimental results, where
scale factor is relevant, but will be against an analytical
solution provided by Pandolfi \& Ortiz \cite{Pandolfi_2012}.} In
\acrshort{mpm}, two different discretization are required. On one
hand, a cartesian grid of nodes is considered with a nodal spacing
value of 0.025. On the other hand, the plate will be modeled with a
initial layout of four particles per element and occupying the Gauss
quadrature positions.\\

@@

\begin{table}
  \centering
  \begin{tabular}[]{c c c c c c c}
    \hline
      &   $\rho$   & $\text{f}_c$ & $\text{f}_t$ & $G_F$ &   E   & $\text{d}_{max}$ \\
      & (kg/m$^3$) &     (MPa)    &     (MPa)    & (N/m) & (GPa) & (mm) \\
    \hline
Value &    2368    &     102.7    &      5.4     &  141  &   31  &  12 \\
    \hline
  \end{tabular}
  \caption[Mechanical properties of thje concrete]{Mechanical
    properties of the high strenght concrete.}
  \label{tab:concrete-properties}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
For the present research, a 2D setting of the experiment has been
adopted. Both the hammer and the concrete beam are explicitly
represented in order to properly capture the impact. Several levels of
discretization were required to assess the objectiveness of the
obtained results. The results here exposed are from a discretization
of 21576 material points and 3943 nodes. To achieve better results, an
unestructured grid layout has been adopted focusing the minimum nodal
spacing, 1.2 mm, in the middle of the beam and in the impact surface
of the hammer. For this simulation, \gls{gamma-lme} was fixed to
1.8, this low value of the regularization parameter smooth high stress
overshots after the impact. Here the stabilization properties of the \acrshort{lme}
described in \cite{Molinos2020} becomes crucial to achieve
non-spurious results. In fact, standard linear element were tested
with unsatisfactory results since grid-crossing occurs in the hammer
head producing non realistic forces.\\

First, the reaction and impact forces are validated against their
experimental counterparts. Since the impact forces applied by the
hammer and the reaction forces at the two supports were experimentally
measured, they are compared with numerical ones in Figure
\ref{fig:Reactions-Forces-impact-test}. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{Figure-impact-test-Forces-Time}
  \caption{Evolution of the reaction forces plotted \textit{versus}
    the imposed displacement for linear interpolation technique and
    the \acrshort{lme} approximants.}
  \label{fig:Reactions-Forces-impact-test}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Note that the general trend of the impact forces was correctly
captured. Observe that in experimental solution the delay between
impact peak and reactions peak does not agree with the numerical
ones. A feasible explanation to this unexpected result can due to a
over-rigidity in the supports. \PNA{Although the traditional \acrshort{mpm} implementation allows collision of two bodies, inaccurate energy conservation is obtained without the implementation of a conservative contact algorithm to reproduce the hammer impact in the beam.
Despite the observed discrepancies, this is out of the scope of this
document, although future research of authors will overcome this
limitation. Similarly, results of support forces will be more
realistic when modelled by a suitable contact algorithm instead of
avoiding any vertical displacement}.\MMP{Navas {\it et al.}
(2017)\cite{Navas_2017_ES} demonstrate the importance of the stiffness
of the support in order to obtain accurate results of the reaction
forces. Interesting contact algorithms within the \acrshort{mpm}
methodology are available in the literature
\cite{Bardenhagen_Contact_2001,XZhang_Contact_2011}.}

Finally, longitudinal stress distribution and crack propagation are
depicted in Figure \ref{fig:Stress-vs-damage-impact-test}. Stress
evolution agrees with the results obtained by \cite{Navas_2017_ES}
under the \acrshort{otm} framework. Two additional considerations about
this results are concerning the interpolation technique. On the one hand,
in the opposite to the \acrshort{ugimp} shape function, \acrshort{lme}
allows unstructured grids. This is a remarkable benefit for this kind
of simulations since the majority of the computational effort is
clearly localised in a tiny region of the domain. On the other
hand, there is the possibility to reduce the shape function support to avoid
a material point in one side of the crack is affected by those in the
other side of the crack. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\subfigure[t = 0.27 ms]{\includegraphics[width=0.83\textwidth]{./Figure-impact-test-Damage-vs-Stress-0005}}
\subfigure[t = 0.36 ms]{\includegraphics[width=0.83\textwidth]{./Figure-impact-test-Damage-vs-Stress-0015}}
\subfigure[t = 0.45 ms]{\includegraphics[width=0.83\textwidth]{./Figure-impact-test-Damage-vs-Stress-0030}}
\caption{Evolution of the stress tensor magnitude for linear
  interpolation (pictures in the left side), and \acrshort{lme}
  (pictures in the right side). Both simulations performed with an
  eigenerosion algorithm.}
\label{fig:Stress-vs-damage-impact-test}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

>>>>

\documentclass[preprint,12pt,a4paper]{elsarticle}
\usepackage{lineno}
% \usepackage{hyperref}
\usepackage{float}
\usepackage{graphicx} % figuras
% \usepackage{subfig}
\usepackage{subfigure} % subfiguras
\usepackage{multirow} 
\usepackage{color}
\usepackage{soul}
\usepackage{cancel}

@@

The simulation of fracture propagation in a more accurate and effective
way can be considered as one of the \PNA{ongoing goals} of the development of novel spatial discretisation methods like meshfree techniques. Some
examples of it are the \acrfull{mpm}
\cite{Schreyer_2002,Chen_2002,Nairn_2003,Zhenmao_2005}, the
\acrfull{efgm} \cite{BELYTSCHKO_1995,BELYTSCHKO_2000,Zhuang_2012,Muthu_2013}, the
\acrfull{sph} \cite{Wang_2020,Wang_2019}, the \acrfull{otm} \cite{Li2010,Li_2012,Pandolfi_2013,Li_2015} or Peridynamics
\cite{HA_2011,RABCZUK_2017} among others. \\

\MMP{Concerning} \acrshort{mpm}, fracture \PNA{has been treated numerically through two different ways}. On the one hand, the ``CRAcks with Material Points (CRAMP)'' is proposed~\cite{Nairn_2003,Nairn_2006}. \PNA{The basis of this methodology consist of the removal of} the restriction
of the single-valued velocity field close to the crack through, at least, two sets of nodes. In this method, different labels are assigned to the material points
and nodes to distinguish if they are in the same side of the crack or
not. Under this approach, crack surface is described with line segments
in 2D and triangle patches in 3D cases. The chosen criteria for crack
propagation is based on such parameters as energy release rate
analysed by Tan \& Nairn (2002)\cite{Nairn_2002}, and the stress
intensity factor or the J-integral discussed by Guo \& Nairn
(2004)\cite{Nairn_2004}. 
On the other hand, the \PNA{foundation} of the second approach is the introduction of failed
material points to describe the crack evolution. In these methods, the
formation of failed points describes the nucleation of cracks, and
thereafter its propagation and branching. Consequently, the position
of the crack does not need to be explicitly stated. This fact represents
significant advantages over the ``CRAMP''. Under this approach, the
prediction of failure evolution is computed with a decohesion model,
which has been discussed by Chen {\it et al.}\cite{Zhenmao_2005} and
Schreyer {\it et al.}\cite{Schreyer_2002}. Successful simulations are provided within the framework of the fracture of brittle materials by Chen {\it et
  al.} \cite{Chen_2002,Chen_2003} and Sulsky \& Schreyer
\cite{Sulsky_2004}.\\

Similar to this approach, Schmidt {\it et al.}
\cite{Schmidt_2009} introduced the concept of eigenfracture, where
crack sets are approximated by means of eigen-deformations, which
enable the material to develop displacement jumps at no cost of local
elastic energy. Later, the eigenerosion approach to brittle fracture
was carried out by Pandolfi {\it et al.}
\cite{Pandolfi_2012,Pandolfi_2013}. \PNA{In this technique, the concept of ``erosion'' of
the material point is depicted, being the material point able to remain intact or become completely failed or eroded, when no loading
capacity is bore}. This method has been successfully applied to simulate high
complex phenomena such as dynamic fragmentation of metals
\cite{Li_2015}. Recently, Zhang {\it et al.}
\cite{Zhang_EE_2020} adopted the eigenerosion to resolve the dynamic
fracture of brittle materials in the \acrshort{mpm}
framework. Nonetheless, when quasi-brittle materials are simulated
though this approach, the results exhibit an overestimation of tensile
stress and strain peaks. Furthermore, since the work of Zhang {\it et al.}
\cite{Zhang_EE_2020} is made with conventional \acrshort{mpm}/\acrshort{gimp}, stress oscillations are to be faced.\\

To overcome the limitations observed in the EigenMPM
\cite{Zhang_EE_2020}, the present research proposes the eigensoftening
algorithm developed by Navas {\it et al.}
\cite{Navas_2017_ES,Navas2018a} for the \acrshort{otm} framework and
engineered for quasi-brittle materials. Inspired in the concept of the
crack band model \cite{Bazant83}, since energy dissipation is performed through the softened (or failed) volume, this methodology is able to capture the gradual rather than abrupt
dissipation of the fracture energy. \PNA{Moreover, in order to mitigate stress
oscillations as well as to deal with tensile instabilities, such those that
occurs when particles crosses an element boundary, the work of Molinos~\etal~\cite{Molinos2020} is followed. The traditional \acrshort{mpm} technique is enhanced through the \acrfull{lme} approximation technique
\cite{Arroyo2006} for the spatial discretisation as well as a explicitly \acrshort{mpm} \acrfull{npc} scheme is derived for the time discretisation.}\\

@@

regularisation o \textit{thermalization} parameter such that for

@@

The failure criterion consist of considering that a material point is failed
when $G_p^{k+1}$ surpasses the critical energy release rate that
measures the material-specific energy, $G_F$. The convergence of this
approach has been analyzed by Schmidt {\it et al.}
(2009)\cite{Schmidt_2009}, who proved that $G_F$ converges to the Griffith
fracture when the discretisation size tends to zero. It is necessary to
point out that, when a material point overpass the critical energy, its
contribution to the internal forces vector is set to zero, but its
contribution to the mass matrix is preserved.\\

@@

neighbourhood of $\vec{x}_p^{k+1}$, the equation 

@@

\DM{The proposed approach to overcome the two main shortcomings of
  EighenMPM \cite{Zhang_EE_2020} has been evaluated with ``three
  benchmark tests''}.
The first one deals with the presence of stress
instabilities provoked by the spatial discretisation, appearing even when the \acrshort{gimp} shape functions are employed. To overcome it, \acrshort{lme}
approximants are introduced as an alternative to the existing interpolation techniques. Its
performance in mitigating spurious stress oscillations under the \acrshort{mpm}~\cite{Wobbes2020,Molinos2020} framework helps to enhance
notoriously the quality of the results as it is observed in Section
\ref{sec:3.1}, where both interpolation techniques
are compared by carrying out an eigenerosion simulation. The second
limitation is concerned to its inability to simulate properly quasi-brittle
fracture \cite{Navas_2018_ES}. It can be solved through the
eigensoftening algorithm described in Section \ref{sec:2.3}.\MMP{A proof
of it is exposed in Sections \ref{sec:3.2} \ref{sec:3.3}, where experimental results
are compared with experimental ones as well as eigensoftening
computations. In the first case comparing with a semicircular bending
test and in the second case with a drop-weight impact test.}

\subsection{Edge-cracked square panel in mode I}
\label{sec:3.1}
The aim of the problem presented hereinafter is to assess the
capability of the \acrshort{lme} approximants to improve the result
\textit{versus} the standard linear interpolation. The application
consists of a square plate of size\MMP{$H = 1\ [L] $} containing an initial edge
crack of length $0.25 \cdot H$ loaded in a pure mode I by displacement
control on the outer flanks of the plate (See Figure
\ref{fig:geometry-cracked-panel-mode-I} for details). 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{Figure-Mode_I}
  \caption{Geometry and boundary condition of the drop-weight impact test.}
  \label{fig:geometry-cracked-panel-mode-I}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The constitutive model considered in the numerical experiment is a
linear-elastic Hookean material, whose Young's modulus \MMP{\gls{E} = 1.06
$[M] [L]^{-1} [T]^{-2}$, the Poisson's ratio \gls{nu} = 0.333, and
critical energy-release rate \gls{Gf} = 0.0001 $[L]^{2} [T]^{-2}$. The absence of units is due to the current simulation will not be validated against experimental results, where
scale factor is relevant, but will be against an analytical
solution provided by Pandolfi \& Ortiz \cite{Pandolfi_2012}.} In
\acrshort{mpm}, two different discretisation are required. On one
hand, a cartesian grid of nodes is considered with a nodal spacing
value of 0.025. On the other hand, the plate will be modeled with a
initial layout of four particles per element and occupying the Gauss
quadrature positions.\\

@@

\begin{table}
  \centering
  \begin{tabular}[]{c c c c c c c}
    \hline
      &   $\rho$   & $\text{f}_c$ & $\text{f}_t$ & $G_F$ &   E   & $\text{d}_{max}$ \\
      & (kg/m$^3$) &     (MPa)    &     (MPa)    & (N/m) & (GPa) & (mm) \\
    \hline
Value &    2368    &     102.7    &      5.4     &  141  &   31  &  12 \\
    \hline
  \end{tabular}
  \caption[Mechanical properties of thje concrete]{Mechanical
    properties of the high strenght concrete.}
  \label{tab:concrete-properties}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
For the present research, a 2D setting of the experiment has been
adopted. Both the hammer and the concrete beam are explicitly
represented in order to properly capture the impact. Several levels of
discretisation were required to assess the objectiveness of the
obtained results. The results here exposed are from a discretisation
of 21576 material points and 3943 nodes. To achieve better results, an
unstructured grid layout has been adopted focusing the minimum nodal
spacing, 1.2 mm, in the middle of the beam and in the impact surface
of the hammer. For this simulation, \gls{gamma-lme} was fixed to
1.8, this low value of the regularization parameter smooth high stress
overshots after the impact. Here the stabilization properties of the \acrshort{lme}
described in \cite{Molinos2020} becomes crucial to achieve
non-spurious results. In fact, standard linear element were tested
with unsatisfactory results since grid-crossing occurs in the hammer
head producing non realistic forces.\\

First, the reaction and impact forces are validated against their
experimental counterparts. Since the impact forces applied by the
hammer and the reaction forces at the two supports were experimentally
measured, they are compared with numerical ones in Figure
\ref{fig:Reactions-Forces-impact-test}. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{figure}
  \centering
  \subfigure[Hammer forces]{\includegraphics[width=0.8\textwidth]{Figure-impact-test-Forces-Time}}
  \subfigure[Reactions]{\includegraphics[width=0.8\textwidth]{Figure-impact-test-Reactions-Time}}
  \caption{Comparison of eigensoftening \textit{versus} experimental results.}
  \label{fig:Reactions-Forces-impact-test}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Note that the general trend of the impact forces was correctly
captured. \PNA{Although the traditional \acrshort{mpm} implementation allows collision of two bodies, inaccurate energy conservation is obtained without the implementation of a conservative contact algorithm to reproduce the hammer impact in the beam.
Despite the observed discrepancies, this is out of the scope of this
document, although future research of authors will overcome this
limitation. Similarly, results of support forces will be more
realistic when modelled by a suitable contact algorithm instead of
avoiding any vertical displacement}.\MMP{Navas {\it et al.}
(2017)\cite{Navas_2017_ES} demonstrate the importance of the stiffness
of the support in order to obtain accurate results of the reaction
forces. Interesting contact algorithms within the \acrshort{mpm}
methodology are available in the literature
\cite{Bardenhagen_Contact_2001,XZhang_Contact_2011}.}

Finally, longitudinal stress distribution and crack propagation are
depicted in Figure \ref{fig:Stress-vs-damage-impact-test}. Stress
evolution agrees with the results obtained by \cite{Navas_2017_ES}
under the \acrshort{otm} framework. Two additional considerations about
this results are concerning the interpolation technique. On the one hand,
in the opposite to the \acrshort{ugimp} shape function, \acrshort{lme}
allows unstructured grids. This is a remarkable benefit for this kind
of simulations since the majority of the computational effort is
clearly localised in a tiny region of the domain. On the other
hand, there is the possibility to reduce the shape function support to avoid
a material point in one side of the crack is affected by those in the
other side of the crack. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\subfigure[t = 0.27 ms]{\includegraphics[width=0.83\textwidth]{./Figure-impact-test-Damage-vs-Stress-0005}}
\subfigure[t = 0.36 ms]{\includegraphics[width=0.83\textwidth]{./Figure-impact-test-Damage-vs-Stress-0015}}
\subfigure[t = 0.45 ms]{\includegraphics[width=0.83\textwidth]{./Figure-impact-test-Damage-vs-Stress-0030}}
\caption{Evolution of the stress tensor magnitude [MPa] for linear
  interpolation (pictures in the left side), and \acrshort{lme}
  (pictures in the right side). Both simulations performed with an
  eigenerosion algorithm.}
\label{fig:Stress-vs-damage-impact-test}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%% Local Variables:
%%% ispell-local-dictionary: "en_GB"
%%% End:
